\documentclass{article}
\usepackage{amsmath}

\begin{document}

\section*{2025 MIT Science Bowl High School Invitational}
\subsection*{Round 5}

\subsubsection*{1) BIOLOGY}
\textbf{TOSS-UP}
Multiple Choice Which of the following states would lead to the highest expression of lac operon?
W) High lactose, high glucose
X) High lactose, low glucose
Y) Low lactose, high glucose
Z) Low lactose, low glucose
ANSWER: X) HIGH LACTOSE, LOW GLUCOSE

\textbf{BONUS}
Short Answer The statoliths (read: stay-toe-liths) that help plant roots sense gravity are specialized versions of what starch-storing plant organelle?
ANSWER: AMYLOPLAST (DO NOT ACCEPT: PLASTID)

\subsubsection*{2) ENERGY}
\textbf{TOSS-UP}
Short Answer The Zhang Lab studied IscB's (read: Is-ck-B's), a family of proteins that cut bacterial DNA. IscB's are the evolutionary ancestors of what protein widely used in CRISPR gene editing?
ANSWER: CAS9

\textbf{BONUS}
Multiple Choice Researchers in the Multicore Algorithms Group at MIT are studying the design of hashable data structures. After a list of prime numbers are added to a hash set, which of the following could not be the product of the hash set's elements?
W) 51
X) 67
Y) 70
Z) 75
ANSWER: Z) 75

\subsubsection*{3) MATH}
\textbf{TOSS-UP}
Short Answer In terms of a single trigonometric function, what is the simplest form of the trigonometric expression $\cot x \sin^{2}x / \cos x$ (read: quantity cotangent of x times quantity sine of x squared divided by quantity cosine of x)?
ANSWER: $\sin x$

\textbf{BONUS}
Short Answer What is the remainder when the polynomial $2x^{4}-3x^{3}+5x-9$ (read: 2 x to the power of 4 minus 3 x cubed plus 5 x minus 9) is divided by the monomial $x - 2$?
ANSWER: 9

\subsubsection*{4) PHYSICS}
\textbf{TOSS-UP}
Short Answer To the nearest radian per second, what is the angular frequency of a wave whose period is 6 seconds?
ANSWER: 1

\textbf{BONUS}
Short Answer A spacecraft initially floating at rest suddenly explodes into two pieces with masses 200 and 400 kilograms, such that each piece receives an impulse of 1500 newton-seconds. After the explosion, what is the relative speed of the two pieces, in meters per second?
ANSWER: 11.25 (ACCEPT: 45/4)

\subsubsection*{5) CHEMISTRY}
\textbf{TOSS-UP}
Multiple Choice A mystery gas effuses through a pinhole three times faster than water vapor at the same temperature. Which of the following could be the identity of the mystery gas?
W) Hydrogen
X) Helium
Y) Carbon dioxide
Z) Sulfur dioxide
ANSWER: W) HYDROGEN

\textbf{BONUS}
Multiple Choice What is the average oxidation state of technetium in the polyoxotechnetate (read: poly-oxo-tech-nuh-tate) ion (read: T-c 20 O 68 four minus)?
W) +6.4
X) +6.6
Y) +6.8
Z) +7
ANSWER: X) +6.6 ($Tc_{20}O_{68}^{4-}$)

\subsubsection*{6) EARTH AND SPACE}
\textbf{TOSS-UP}
Multiple Choice In which season of the Northern Hemisphere do atmospheric carbon dioxide concentrations typically peak?
W) Winter
X) Spring
Y) Summer
Z) Fall
ANSWER: X) SPRING

\textbf{BONUS}
Multiple Choice If Earth abruptly stopped rotating, which of the following best describes how global atmospheric circulation patterns would most likely change?
W) Intensified three-cell circulation due to stronger pressure gradients
X) Weakened three-cell circulation due to weaker pressure gradients
Y) Single cell per hemisphere with rising air at the equator and sinking at the poles
Z) Single cell per hemisphere with rising air at the poles and sinking at the equator
ANSWER: Y) SINGLE CELL PER HEMISPHERE WITH RISING AIR AT THE EQUATOR AND SINKING AT THE POLES

\subsubsection*{7) PHYSICS}
\textbf{TOSS-UP}
Short Answer A seesaw, 6 meters long, has beavers sitting on opposite ends with masses of 20 and 30 kilograms, respectively. In newton-meters and rounded to the nearest integer, what is the magnitude of the net torque exerted on the seesaw about its midpoint?
ANSWER: 294

\textbf{BONUS}
Short Answer A solid and uniformly dense sphere has a mass of 10 kilograms and a radius of 3 meters. In kilogram meters squared, what is the moment of inertia of the sphere about an axis tangent to its surface?
ANSWER: 126

\subsubsection*{8) CHEMISTRY}
\textbf{TOSS-UP}
Multiple Choice Which of the following quantum numbers could be equal to -1 for an electron occupying an atomic orbital?
W) Principal
X) Azimuthal
Y) Magnetic
Z) Spin
ANSWER: Y) MAGNETIC

\textbf{BONUS}
Short Answer Rank the following three types of unit cells by increasing packing efficiency: 1) Body-centered cubic; 2) Simple cubic; 3) Hexagonal close packed.
ANSWER: 2, 1, 3

\subsubsection*{9) MATH}
\textbf{TOSS-UP}
Short Answer Two vertices of a regular decagon are selected at random. What is the probability that the segment connecting them is not one of the sides of the decagon?
ANSWER: $7/9$

\textbf{BONUS}
Short Answer How many four digit positive integers satisfy the property that the product of their digits is 2025?
ANSWER: 6

\subsubsection*{10) EARTH AND SPACE}
\textbf{TOSS-UP}
Multiple Choice In which of the following rock types are subterranean rivers most commonly embedded?
W) Limestone
X) Sandstone
Y) Granite
Z) Shale
ANSWER: W) LIMESTONE

\textbf{BONUS}
Short Answer Order the following three gems by increasing hardness on the Mohs hardness scale: 1) Topaz; 2) Diamond; 3) Pearls.
ANSWER: 3, 1, 2

\subsubsection*{11) BIOLOGY}
\textbf{TOSS-UP}
Short Answer Plant cells do not lyse in a hypotonic environment due to the prescence of what cellulose-containing structure?
ANSWER: CELL WALL

\textbf{BONUS}
Multiple Choice Which of the following DNA strands, if annealed with their complementary strand, would have the lowest melting point?
W) TTAGAAT
X) ACTCAGA
Y) ACTACGT
Z) GCGCCTT
ANSWER: W) TTAGAAT

\subsubsection*{12) ENERGY}
\textbf{TOSS-UP}
Short Answer Scientists at the Whitehead Institute have been using fluorinated glucose to study brown fat as a potential use for starving cancer of glucose. What imaging technique did the scientists use to track radioactive fluorinated glucose throughout the body?
ANSWER: POSITRON EMISSION TOMOGRAPHY (ACCEPT: PET)

\textbf{BONUS}
Short Answer MIT scientists discovered both L and D forms of amino acids in samples recently collected by NASA from an asteroid. What type of isomerism relates the L and D forms of an amino acid?
ANSWER: ENANTIOMERISM (ACCEPT: STEREO, STEREOISOMERISM, OPTICAL, OPTICAL ISOMERISM, DO NOT ACCEPT: GEOMETRIC)

\subsubsection*{13) MATH}
\textbf{TOSS-UP}
Short Answer Bronya has a weighted six-sided die, where the probability of rolling each face is proportional to the number on the face. What is the probability that Bronya rolls a one?
ANSWER: $1/21$

\textbf{BONUS}
Short Answer The $log^{*}$ (read: log star) operation, often known as the binary iterated logarithm, is the number of times a base two logarithm must be applied to a number until it is less than or equal to 1. What is the smallest positive integer such that when the $log^{*}$ operation is applied, the result is 4?
ANSWER: 17

\subsubsection*{14) BIOLOGY}
\textbf{TOSS-UP}
Multiple Choice Elk often live in groups, and the male is highly ornamented while the females are not highly ornameted. Knowing this, what kind of mating system do elk likely follow?
W) Monogamy
X) Polyandry
Y) Polygyny (read: puh-LIH-jih-nee)
Z) Promiscuity
ANSWER: Y) POLYGYNY (READ: PUH-LIH-JIH-NEE)

\textbf{BONUS}
Multiple Choice Which of the following processes is least likely to be disrupted by the introduction of a calcium chelator?
W) Formation of a fertilization envelope in a zygote
X) Action potential initiation in a sensory neuron
Y) Long term potentiation in the brain
Z) Peristalsis in the small intestine
ANSWER: X) ACTION POTENTIAL INITIATION IN A SENSORY NEURON

\subsubsection*{15) CHEMISTRY}
\textbf{TOSS-UP}
Multiple Choice Which of the following molecules is nonpolar?
W) Chlorine trifluoride
X) Phosphorus trifluoride
Y) Chlorine pentafluoride
Z) Phosphorus pentafluoride
ANSWER: Z) PHOSPHORUS PENTAFLUORIDE

\textbf{BONUS}
Multiple Choice Cations with which of the following properties will be hydrated by the most water molecules in aqueous solution?
W) Small ionic radius and low charge
X) Small ionic radius and high charge
Y) Large ionic radius and low charge
Z) Large ionic radius and high charge
ANSWER: X) SMALL IONIC RADIUS AND HIGH CHARGE

\subsubsection*{16) PHYSICS}
\textbf{TOSS-UP}
Multiple Choice Which of the following configurations of quarks has the same net charge as a proton?
W) 3 up quarks
X) 2 up quarks and 1 down quark
Y) 1 up quark and 2 down quarks
Z) 3 down quarks
ANSWER: X) 2 UP QUARKS AND 1 DOWN QUARK

\textbf{BONUS}
Multiple Choice Mingwen is moving toward a stationary loudspeaker, while Yufei remains stationary. If Yufei hears a constant pitch from the loudspeaker, which of the following statements must be true?
W) Mingwen observes a higher amplitude sound wave than Yufei
X) Mingwen observes a lower amplitude sound wave than Yufei
Y) Mingwen observes a higher frequency sound wave than Yufei
Z) Mingwen observes a lower frequency sound wave than Yufei
ANSWER: Y) MINGWEN OBSERVES A HIGHER FREQUENCY SOUND WAVE THAN YUFEI

\subsubsection*{17) EARTH AND SPACE}
\textbf{TOSS-UP}
Multiple Choice Relative to a cluster's main sequence turnoff point, where on an H-R diagram are blue stragglers found?
W) Up and to the left
X) Up and to the right
Y) Down and to the left
Z) Down and to the right
ANSWER: W) UP AND TO THE LEFT

\textbf{BONUS}
Short Answer Order the following three energy densities by the time at which they began to dominate the universe's expansion history, from earliest to latest: 1) Dark energy; 2) Matter; 3) Radiation.
ANSWER: 3, 2, 1

\subsubsection*{18) ENERGY}
\textbf{TOSS-UP}
Multiple Choice Astronomers at the Kavli Institute observed an ancient lonely quasar. Where would a quasar be found?
W) Outer edge of a planetary ring system
X) Arm of a spiral galaxy
Y) Remnant of a gamma ray burst
Z) Bright core of a galaxy
ANSWER: Z) BRIGHT CORE OF A GALAXY

\textbf{BONUS}
Multiple Choice The Freedman Lab synthesized a strongly correlated spin glass with completely aligned electron spin domains. What type of magnetism does this spin glass exhibit?
W) Paramagnetism
X) Diamagnetism
Y) Ferromagnetism
Z) Anti-ferromagnetism
ANSWER: Y) FERROMAGNETISM

\subsubsection*{19) MATH}
\textbf{TOSS-UP}
Multiple Choice Which of the following 3D shapes represents the locus of all points equidistant from a line?
W) Cylinder
X) Sphere
Y) Ellipsoid
Z) Paraboloid
ANSWER: W) CYLINDER

\textbf{BONUS}
Short Answer What percentage of 45 is equal to 65% of 18?
ANSWER: 26

\subsubsection*{20) PHYSICS}
\textbf{TOSS-UP}
Short Answer When a sound wave is emanated isotropically from a point source, the intensity of the wave is linearly proportional to what power of the distance from the point source?
ANSWER: -2

\textbf{BONUS}
Short Answer Mario travels along the x-axis. His momentum $p(t)$ (read: p of t) can be modeled as a function of time, where $p(t)=-2t^{3}+9t^{2}-12t+1$. At what time t is the net force experienced by Mario most positive?
ANSWER: 3/2 (ACCEPT: 1.5)

\subsubsection*{21) CHEMISTRY}
\textbf{TOSS-UP}
Short Answer How many sigma bonds are formed in one molecule of ethane?
ANSWER: 7

\textbf{BONUS}
Short Answer Identify all of the following three rotational symmetries that are present in a ground-state benzene molecule: 1) Two-fold; 2) Three-fold; 3) Four-fold.
ANSWER: 1 AND 2

\subsubsection*{22) ENERGY}
\textbf{TOSS-UP}
Multiple Choice Economists at MIT routinely use linear regression to model datasets. Which of the following coefficients of determination describes a linear regression model with the best goodness of fit?
W) -0.1
X) 0.2
Y) 0.5
Z) 0.8
ANSWER: Z) 0.8

\textbf{BONUS}
Multiple Choice Physicists at the MIT-Harvard Center for Ultracold Atoms cooled lithium-6 atoms to nanokelvin temperatures so they could observe frictionless resonance in what resulting state of matter?
W) Plasma
X) Superfluid
Y) Ferromagnet
Z) Bose-Einstein Condensate
ANSWER: X) SUPERFLUID

\subsubsection*{23) BIOLOGY}
\textbf{TOSS-UP}
Short Answer Golden Gate and Gibson assembly both use what class of bacterial enzymes to cleave DNA fragments for plasmid assembly?
ANSWER: RESTRICTION ENZYME

\textbf{BONUS}
Short Answer Identify all of the following three vitamins that would be excreted in urine in significant amounts: 1) Thiamine; 2) Niacin; 3) Ascorbic acid.
ANSWER: ALL

\subsubsection*{24) EARTH AND SPACE}
\textbf{TOSS-UP}
Short Answer Identify all of the following three anomalies that were caused by giant impacts: 1) Mars' crust is thinner in the northern than southern hemisphere; 2) Mercury has a disproportionately large iron core; 3) Uranus has a high obliquity to the ecliptic.
ANSWER: ALL

\textbf{BONUS}
Short Answer Order the following three regions in order of increasing aggregate mass: 1) The asteroid belt; 2) The Kuiper belt; 3) The Oort cloud.
ANSWER: 1, 2, 3

\subsubsection*{25) PHYSICS}
\textbf{TOSS-UP}
Short Answer Madeline is traveling at a constant 30 meters per second when she passes a cop car at rest. At that instant, the cop begins accelerating in pursuit at 5 meters per second squared. In seconds, how long will the cop take to catch up to Madeline?
ANSWER: 12

\textbf{BONUS}
Short Answer Using scientific notation to one significant figure and in Joules, what is the energy of an object with a rest mass of 1 kilogram?
ANSWER: $9\times10^{16}$ (READ: NINE TIMES TEN TO THE SIXTEENTH POWER)

\end{document}